\documentclass{article}

\title{CSE475 Mid-game Strategy}
\author{Team Win: Ben Chavet, Justin McKinstry, Steve Mott}
\date{\today}

\begin{document}
\maketitle

Due to the fact that we have already spent half of our money, we have decided
to change our strategy.  We will only enter two of the five auctions on the
second day, the English Auction and the Vickrey Auction.

Our utility for the English Auction is significantly higher than the market
value for the item, so we are assuming that we have at least one of the
higher utilities for this item.  Therefore, we believe that it is worth
entering this auction with the expectation of winning the item.

We intend to be conservative in our bidding, only incrementing the highest
bid by \$1.  By doing this, we will not pay any higher than what the competing
bidders are willing to pay.  This also allows us to hide the fact that we
intend to win this item.

In the Vickrey Auction, our utility is also relatively higher than the
market value for the item.  However, it is not so much higher that we can
assume that we have one of the highest utilities for the item.  Because
of this, we plan to bid higher than our utility in hopes of preventing
another team from winning the bid.

What we bid will depend on how much we end up paying for the item in the 
English Auction.  We plan on bidding whatever cash we have left, up to
the value that would make us break even over all.  This way we do not lose
any utility, and at the same time we would keep a team with a higher utility
from gaining the item, and only pay what they bid.

This is a more aggressive approach, but being the last auction of the game,
we are willing to sacrifice a little utility in order to keep another team
from getting more utility than we would have received.


\end{document}