\documentclass{article}

\title{CSE475 Gameday \#3 Strategy}
\author{Team Win: Ben Chavet, Justin McKinstry, Steve Mott}
\date{\today}

\begin{document}
\maketitle

\section{Blackboard Strategy}

There are a few things that we need to keep in mind during this round.
First, we have to be very clear in our communication, otherwise we may
lose meaning since we do not have the benefit of using hand gestures.
Next, if reporting is free, a high level of verbosity is preferred
because the more information we have, the easier it is to utilize it.
And, finally, items may be ranked on their utility, but they can also
be ranked by how difficult they are to find.  Any items that are very
difficult to find will have a higher potential worth towards the end of
the round, especially to agents that want to maximize their goals.

That said, our strategy is fairly straightforward.  Whenever we find
one of our own items, we pick it up, regardless of its value.  If we
find an item belonging to another team, we call it in to be posted on
the blackboard.  The price we post for each item is based on the
estimated utility as well as how difficult it was to find.

Cost of communication may be a hindrance to this plan.  If each call
costs us money, we need to gather as much information as possible
before we make easy call.  If each post on the blackboard costs money,
we need to pick our prices in a very stable manner in order to profit
on as many posts as possible without hurting ourselves in the long run.

\section{Negotiation Strategy}

There are some differences in this round that need to be taken into
account.  First, communication amongst team members is less of an issue,
but it is more difficult to successfully negotiate with other agents.
Next, the opportunity to sell items is greatly reduced, as we must be
face-to-face with each group we want to negotiate with.  Finally,
the difficulty of finding an item plays a smaller part as there are
more people roaming around, and more opportunity to observe where
everyone is looking.

Our strategy for this round is similar to what we are doing in the
Blackboard round.  If we find one of our items, we pick it up, and
if we find an item belonging to another group, we take note of it for
later negotiations.  In addition, we will attempt to be discrete about
when and where we find any items in order to minimize other agents'
knowledge base.  Finally, we will put more emphasis on finding our
own items, rather than negotiating with other teams about where to
find them.

\end{document}